\documentclass{article}
\usepackage{graphicx} % Required for inserting images
\usepackage{textcomp}
\newcommand{\forceindent}{\leavevmode{\parindent=1em\indent}}


\title{AI proj 2}
\author{DANIEL TEYTEL, Long Tran}
\date{February 2023}

\begin{document}

\maketitle

\section{Introduction}
\begin{enumerate}
\item[1:]    
(Mchadia, 311, 70, 241)

(Drobeta, 387, 145, 242)

(Craiova, 425, 265, 160)

(Timisoara, 440, 111, 329)

(Pitesti, 503, 403, 100)

(Bucharest, 504, 504, 0)

\item[]
Problem 2 (10 points): Consider a state space where the start state is number 1 and each state k has two successors: numbers 2k and 2k + 1.

(a) Suppose the goal state is 11. List the order in which states will be visited for breadth-first search, depth-limited search with limit 3, and iterative deepening search.

\textit{Assume for each iteration, algorithms will pick the lowest values in the available items list}

\textbf{Bread-first Search}
Pick s(1) \verb|->| expand s(2), s(3) \\
\forceindent Pick s(2) \verb|->| expand s(4), s(5) \\
\forceindent Pick s(3) \verb|->| expand s(6), s(7) \\
\forceindent\forceindent Pick s(4) \verb|->| expand s(8), s(9) \\
\forceindent\forceindent Pick s(5) \verb|->| expand s(10), s(11) \verb|->| find target 11 \verb|->| program done.\\

\textbf{Depth-limited Search with 3}

Search is limited with max depth is 3. Suppose s(1) is depth 0.

\#1 Pick s(1) \verb|->| s(2) \verb|->| s(4) \verb|->| s(8) \\
\#1.2 Pick s(1) \verb|->| s(2) \verb|->| s(4) \verb|->| s(9) \\
\#1.3 Pick s(1) \verb|->| s(2) \verb|->| s(5) \verb|->| s(10) \\
\#1.4 Pick s(1) \verb|->| s(2) \verb|->| s(5) \verb|->| s(11) \verb|->| Find target \\
\verb|->| Program done.

\textbf{Iterative Deepening Search}

\textbf{Limit = 1}\\
s(1) \verb|->| s(2)\\
s(1) \verb|->| s(3)\\
\verb|->| Reached limit


\textbf{Limit = 2}\\
s(1) \verb|->| s(2) \verb|->| s(4)\\
s(1) \verb|->| s(2) \verb|->| s(5)\\
s(1) \verb|->| s(3) \verb|->| s(6)\\
s(1) \verb|->| s(3) \verb|->| s(7)\\
\verb|->| Reached limit

\textbf{Limit = 3}\\
\#1 Pick s(1) \verb|->| s(2) \verb|->| s(4) \verb|->| s(8) \\
\#1.2 Pick s(1) \verb|->| s(2) \verb|->| s(4) \verb|->| s(9) \\
\#1.3 Pick s(1) \verb|->| s(2) \verb|->| s(5) \verb|->| s(10) \\
\#1.4 Pick s(1) \verb|->| s(2) \verb|->| s(5) \verb|->| s(11) \verb|->| Find target \\
\verb|->| Program done.

(b) How well would bidirectional search work on this problem? List the order in which states will be visited. What is the branching factor in each direction of the bidirectional search?

\item[]
Problem 3 (5 points): Which of the following statements are correct and which ones are wrong?

(a) Breadth-first search is a special case of uniform-cost search.

True

(b) Depth-first search is a special case of best-first tree search.

Wrong

(c) Uniform-cost search is a special case of A∗search.

True, if setting h(i) = 0 for each n.

(d) Depth-first graph search is guaranteed to return an optimal solution.

Wrong, it is bounded by max depth of the problem and may run infintely

(e) Breadth-first graph search is guaranteed to return an optimal solution.

True

(f) Uniform-cost graph search is guaranteed to return an optimal solution.

True

(g) A∗ graph search is guaranteed to return an optimal solution if the heuristic is consistent.

True

(h) A∗ graph search is guaranteed to expand no more nodes than depth-first graph search if the heuristic is consistent.

False, in best case, depth-first search find optimal solution in first path try.

(i) A∗ graph search is guaranteed to expand no more nodes than uniform-cost graph search if the heuristic is consistent.

True
\end{enumerate}

\end{document}
